From Object Classification to Naming: Modeling Entry-level Names for Real-world Objects

### 2019-12-10 papers/ACL2020/acl2020_main.tex
a get-it-done-conclusion

\section{Conclusions}
\label{sec:conclusions}

>>>>

\section{Conclusions}
\label{sec:conclusions}
In this paper, we have investigated instance-level entry-level naming of objects in images.
To the best of our knowledge, our work is the first to investigate entry-level naming on such a large-scale but thorougly verified empirical basis, 
as opposed to previous works that mostly adopted a strictly taxonomic view of naming.
For models in \lv, the complexity of human naming data we observed brings up an important question: how should a naming models best finetune and calibrate the \textit{vocabulary} of object detection and classification models from Computer Vision, in order to capture natural naming behavior?
We showed that the best way to achieve this is to first retrain an object detector on a large set of \arbitrary names and then finetune via transfer learning to entry-level names. 
In future work, we plan to develop this approach further and assess, e.g., how well the learned naming vocabulary generalizes for other, external datasets.
We also showed that naming data elicited for boxed objects comes with certain challenges, which have to be considered during evaluation (and potentially during modeling). 
%Bounding boxes are not always clear enough pointers to objects, and at the same time there is no clear line between other object mistakes (\textit{batter-helmet}), referential disagreements (\textit{bed-sleeping bag}, when the two visually overlap in the image), and valid alternatives (\textit{carpet-floor} can be a metonymy).
%Future work will need to address these challenges.
